Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-05-16 GWLDCII.tex
through case I of 3.13

We first calculate \hlfix{$I^{W}_w(?)$}{which prop(s), as a function?} for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range, {\color{violet}(if $r \neq p$, $I_w^W(r) = I_w^V(r)$)} while the value of $I^{W}_w(p)$ depends on \st{how soon $q$ is assigned to a vertex, i.e. on}\sanote{don't like the phrasing ``soon''} the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the \hlfix{majority}{$w \in [l, l+a-1]$} of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by \hlfix{$I_w^{W}$, then the remainder of $I_w^{W}$}{algorithm instead of $I_w^W$?} proceeds identically to the assignments of $I^{V}_{w+1}$.  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in the second case of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

Suppose for a contradition that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.  Fix $n$.  Let the triple $(W, i, m)$ be such a counterexample on $n$ vertices which is minimal with respect to the number of propagators. %, and among all those counterexamples on $n$ vertices with the same number of propagators, let $(W,i,k)$ be minimal with respect to the distance from $i$ to $k$ in the $\leq _i$ order.

@@

Now suppose that $i \in I_i$.  Let $p$ be the propagator which contributes $i$ to $I_i$; thus one end of $p$ must lie on either edge $i-1$ or edge $i$.  In both cases let $b$ denote the edge supporting the other end of $p$.

\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.  Then $p$ is not supported on $i+1$, so in building $I_{i+1}$ we will take the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$.  Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ is taken at vertex $b$, as otherwise $b$ would never be contributed by $p$.    Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any unassigned propagators remaining that are before $p$.  This is also true in when the algorithm constructing $I_i$ reaches $b$, since the same propagators have been assigned beforehand.  Finally, we also note that $m\geq_i b+1$.

@@

By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm; the propagators we assigned in the latter case are exactly the ones removed to build $W'$.  Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.  This gives the equations
\begin{align*}
  I_i^{W} \cap [b,i-1] & = I_b^{W'} \\
  I_{i+1}^{W} \cap [b+1,i-1] & = I_{b+1}^{W'}
\end{align*}
where the diagram is indicated in the superscript.
Thus we have $m\in I_b^{W'}\setminus\{b\}$ and $m\not\in I_{b+1}^{W'}$, contradicting the minimality of $(W, i, m)$.

>>>>

We first calculate \hlfix{$I^{W}_w(?)$}{which prop(s), as a function?} for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range, {\color{violet}(if $r \neq p$, $I_w^W(r) = I_w^V(r)$)} while the value of $I^{W}_w(p)$ depends on \st{how soon $q$ is assigned to a vertex, i.e. on}\sanote{don't like the phrasing ``soon''} the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the \hlfix{majority}{$w \in [l, l+a-1]$} of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by \hlfix{$I_w^{W}$, then the remainder of $I_w^{W}$}{$I_w$ instead of $I_w^W$?} proceeds identically to the assignments of $I^{V}_{w+1}$.  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
       \end{cases}
       \]
If $j$ is not in the support of $p$, then we must be in the second case of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

Suppose for a contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.  Fix $n$.  Let the triple $(W, i, m)$ be such a counterexample on $n$ vertices which is minimal with respect to the number of propagators. %, and among all those counterexamples on $n$ vertices with the same number of propagators, let $(W,i,k)$ be minimal with respect to the distance from $i$ to $k$ in the $\leq _i$ order.

@@

Now suppose that $i \in I_i$.  Let $p$ be the propagator which contributes $i$ to $I_i$, that is, {\color{violet} $I^W_i(p) = i$}; thus one end of $p$ must lie on either edge $i-1$ or edge $i$.  In both cases let $b$ denote the edge supporting the other end of $p$, {\color{violet}that is, $p = (i, b)$ or $p = (i-1, b)$.}
\sanote{We use taking and contributing interchangably. Do we want to normalize? I vote for contributing}

\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.  Then $p$ is not supported on $i+1$, so in building $I_{i+1}$ \hlfix{we will take the same propagators as in the construction of $I_i$}{what does this mean? Isn't it possible to take the same propagators but in a different order to get different numbers? If not, is there a proof?} \hlfix{from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$}{is this the same fact that is used without proof in 3.11?}.  Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ is taken \st{at} {\color{violet} by?} vertex $b$, as otherwise $b$ would never be contributed by $p$. Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any unassigned propagators remaining that are \hlfix{before}{do we have an ordering on $\cP$?} $p$.  This is also true in when the algorithm constructing $I_i$ reaches $b$, since the \hlfix{same propagators have been assigned beforehand}{see above.}.  Finally, we also note that $m\geq_i b+1$.

@@

By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm {\color{violet}(recall that $I^W_i(p) =i$)}\st{; the propagators we assigned in the latter case}{\color{violet}. The propagators contributing to $I_{i}$ for $W$ before the vertex $b$} are exactly the ones removed to build $W'$.  Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.  This gives the equations
\begin{align*}
  I_i^{W} \cap [b,i-1] & = I_b^{W'} \\
  I_{i+1}^{W} \cap [b+1,i-1] & = I_{b+1}^{W'}
\end{align*} \sanote{ $I_i^{W}$ is a map not a $k$-tuple. Do we mean $I_i$ for $W$? or $I_i^{W}(\cP)$ because we want the image set?}
where the diagram is indicated in the superscript.
Thus we have $m\in I_b^{W'}\setminus\{b\}$ and $m\not\in I_{b+1}^{W'}$, contradicting the minimality of $(W, i, m)$.
